\begin{thebibliography}{}

\bibitem{ullman}
Aho, A. V. and J. D. Ullman. 1972. \textit{The Theory of Parsing,
        Translation, and Compiling}, volume 1. Prentice Hall.

% not used
\bibitem{multiCCA}
Ammar et al. 2016. \textit{Massively multilingual word embeddings}.
        arXiv:1602.01925v2.

\bibitem{malopa}
Ammar et al. 2016. \textit{Many Languages, One Parser}. arXiv: 1602.01595v4

\bibitem{balCompGrammar}
Bal B. K., Rupakheti P. and Khatiwada L. P. 2008. \textit{Report on
        Nepali Computational Grammar}

% not used
\bibitem{balStructureGrammar}
Bal B. K. 2004. \textit{Structure of Nepali Grammar}

\bibitem{paninianEng}
Bharati et al. 1996. \textit{Paninian Grammar Framework Applied to
        English}

% not used
\bibitem{cotraining}
Blum A., Mitchell T. 1998. \textit{Combining Labeled and Unlabeled Data with Co-Training} % INSERT PUBLICATION HERE %

\bibitem{chen}
Chen, D. and C. Manning. 2014. \textit{A fast and accurate dependency
        parser using neural networks}. EMNLP

\bibitem{multiEmbedding}
Chen et al. 2018. \textit{Unsupervised Multilingual Word Embeddings}. arXiv:1808.08933

\bibitem{chomsky}
Chomsky, N. 1956. \textit{Three models for the description of language}. IRE Transactions on Information Theory, 2(3):113–124.

\bibitem{vietnamese}
Duc D. et al. 2021. \textit{Adapting Word Order Transformation for Vietnamese Dependency Parsing}. IEEE RIVF International Conference on Computing and Communication Technologies.

\bibitem{stackLstm}
Dyer et al. 2015. \textit{Transition-based dependency parsing with
        stack LSTM}. In Proc. of ACL.

\bibitem{steps-parser}
Gruenewald S. et al. 2021. \textit{Applying Occam’s Razor to Transformer-Based Dependency Parsing: What Works, What Doesn’t, and What is Really Necessary}. IWPT 2021.

\bibitem{robustProjection}
Guo et al. 2016. \textit{A representation learning framework for multi-source transfer parsing}. In Proc. of AAAI.

\bibitem{bistm}
Jaf S., and Calder C. \textit{Deep Learning for Natural Language Parsing}. IEEE Access.

% note used
\bibitem{tiedemann}
Joerg Tiedemann. 2015. \textit{Cross-lingual dependency parsing with universal dependencies and predicted POS labels}. In Proc. of DepLing.

\bibitem{stanfordLec}
Jurafsky D., James H. Martin (2021) \textit{Stanford Notes on Speech and Language Processing}

\bibitem{bistParser}
Kiperwasser E. and Goldberg Y. 2016. \textit{Simple and Accurate Dependency Parsing Using Bidirectional LSTM Feature Representations}. Transactions of the Association for Computational Linguistics, 4:313--327

% not used
\bibitem{nepvec}
Koirala P., Niraula N. B. 2021. \textit{NPVec1: Word Embeddings for Nepali - Construction and Evaluation}. Proceedings of the 6th Workshop on Representation Learning for NLP (RepL4NLP-2021).

\bibitem{multilingualCaseStudy}
Lim, KyungTae et al. 2018. \textit{Multilingual Dependency Parsing for
Low-Resource Languages: Case Studies on North Saami and
{K}omi-{Z}yrian}. Proceedings of the Eleventh International Conference on
Language Resources and Evaluation

\bibitem{lang2vec}
Malaviya C. et al. 2017. \textit{Learning Language Representations for Typology Prediction}. arXiv:1707.09569v1

\bibitem{penn}
Marcus et al. 1993. \textit{Building A large Annotated Corpus of English: The Penn Treebank}. Association for Computational Linguistics.

\bibitem{compareRuleStatistical}
Meurers D. et al. 2011. \textit{Comparing Rule Based and Data-Driven Dependency Parsing of Learner Language}. Frontiers in Artificial Intelligence and Applications.

\bibitem{nivreUD}
Nivre J. et al. 2018 \textit{Universal dependencies 2.3}, LINDAT/CLARIN
digital library at the Institute of Formal and Applied Linguistics (UFAL),
Faculty of Mathematics and Physics, Charles University.

\bibitem{nivre1}
Nivre, J. 2003. \textit{An efficient algorithm for projective dependency parsing}. Proceedings of the 8th International Workshop on Parsing Technologies (IWPT).

\bibitem{tamilDep}
Ramasamy L. et al. 2011. \textit{Tamil Dependency Parsing: Results Using Rule Based and Corpus Based Approaches}. Computational Linguistics and Intelligent Text Processing.

\bibitem{semiSupervised1}
Sagae, K., Tsujii, J. 2007. \textit{Dependency parsing and domain adaptation with LR models and
parser ensembles}. In Proceedings of the CoNLL shared task session of EMNLP-CoNLL, Prague
(pp. 1044–1050)

% not used
\bibitem{dropout}
Srivastava et al. 2014. \textit{Dropout: A simple way to prevent neural networks from overfitting.}. Journal of machine Learning Reearch, 15(1):1929-1958.

\bibitem{semiSupervised2}
Suzuki, J. et al. 2011. \textit{Learning condensed feature representations from
large unsupervised data sets for supervised learning}. In Proceedings of ACL, Portland (pp. 636–
641). Association for Computational Linguistics.

\bibitem{zero-shot}
Tran Ke et al. 2019. \textit{Zero-shot Dependency Parsing with Pre-trained
Multilingual Sentence Representations}. Proceedings of the 2nd Workshop on Deep
Learning Approaches for Low-Resource NLP (DeepLo).

\bibitem{udapter}
Ustun A. et al. 2020. \textit{UDapter: Language Adaptation for Truly Universal Dependency Parsing}. arXiv:2004.14327v2

\bibitem{unsupervisedDP}
Wenjuan H. et al. 2019. \textit{Lexicalized Neural Unsuperised Dependency Parsing.}. Neurocomputing, Volume 349.

\bibitem{yajnik1}
Yajnik et al. 2015. \textit{Parsing Techniques using Paninian Framework on Nepali Language}

\bibitem{yajnik2}
Yajnik et al. 2019. \textit{Parsing in Nepali Language Using Linear Programming Problem}

\end{thebibliography}

